Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-05-31 Manuscript.Rmd
make figure headline optional at the end

<!-- NOTES: 
- If you're using Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
- This script is set so you can run each code snippet independently (after you run the setups and data loading snippets above the institutional affiliations)
- Numbers on each chunk correspond generally to sections in the preregistrations (https://osf.io/2rsgm/registrations)
-->

@@

## figures at the end of the manuscript?
figsEnd <- TRUE

@@

## Figures

>>>>

<!-- NOTES: 
- If you're using Rstudio on a mac, you can press 'ctrl + option + o' to compress all chunks and look at the paper + code outline. 
- This script is set so you can run each code snippet independently (after you run the setups and data loading snippets above the institutional affiliations)
- Numbers on each chunk correspond generally to sections in the preregistrations (https://osf.io/2rsgm/registrations)
- Within the Setups chunk, the 'figsEnd' variable dictates whether figs are shown at the end (T) or intermixed in the text (F)
-->

@@

## figures at the end of the manuscript?
figsEnd <- F

@@

`r if(figsEnd){"## Figures"}`
